Delocalization of Eigenvectors in Random Matrices

### 2025-03-24 Draft.tex
stopping times fix

\noindent In our analysis, we will utilize the flow method (\hyperref[sec:flow]{Section 3}), where the spectral parameter $z=E+i\eta$ of the resolvent of $H$ (defined in \hyperref[sec:prereq]{Section 2}) is varied at constant-speed in the upper-half plane $\mathbb{H}$ ($E\in\mathbb{R}$ and $\eta>0$) as the entries of $H$ are realized as Brownian motion \cite{bandSDE}. Two key assumptions we will make are that $\eta \asymp W^2 N^{-2}$ and $\eta\geq W^{-3/4+\eta}$ for some $\eta>0$.

@@

\subsection*{Stieltjes transform identities}
Let us establish several facts and lemmas that we will need throughout our later work. We can begin by observing that: $$m(z)(m(z)+z) = \frac{1}{4}(-z+\sqrt{z^2-4})(z+\sqrt{z^2-4})=\frac{1}{4}(-z^2+z^2-4)=-1$$
$$\Rightarrow |m(z)| = \frac{1}{|m(z)+z|^{-1}}$$
Now, take the imaginary part of $(2)$: $$\text{Im}(m(z)) + \text{Im}\left(\frac{1}{m(z)}\right)+\eta=0$$
We can calculate the second term by simply expanding: $$\frac{1}{m(z)} = \frac{1}{\text{Re}(m(z))+\text{Im}(m(z))i} = \frac{\text{Re}(m(z))-\text{Im}(m(z))i}{|m(z)|^2}\Leftrightarrow \text{Im}\left(\frac{1}{m(z)}\right) = -\frac{\text{Im}(m(z))}{|m(z)|^2}$$
$$\Rightarrow\text{Im}(m(z)) + \text{Im}\left(\frac{1}{m(z)}\right)+\eta=\text{Im}(m(z)) -\frac{\text{Im}(m(z))}{|m(z)|^2}+\eta=0$$
$$\Rightarrow \text{Im}(m(z))\left(1-\frac{1}{|m(z)|^2}\right)=-\eta$$
And since $\text{Im}(m(z))>0$ and $\eta>0$, we must have:
\begin{equation*}\label{2.1} 1-\frac{1}{|m(z)|^2}<0\quad \Leftrightarrow\quad |m(z)|<1, \tag{2.1}
\end{equation*}
which is also equivalent to $\text{Im }m \asymp 1$, where $\asymp$ means being bounded above and below up to a fixed, positive factor. Furthermore, let us rewrite the latter equation as the following two identities: \begin{equation*}\label{2.2}1-|m(z)|^2 = \frac{\eta|m(z)|^2}{\text{Im}(m(z))}
\tag{2.2}
\end{equation*}
\begin{equation*}\label{2.3}\text{Im}(m(z))= \frac{\eta|m(z)|^2}{1-|m(z)|^2 }
\tag{2.3}
\end{equation*}
Now, let $E\in [-10, 10]$ and $\eta\in (0, 10]$. First, we claim that $|m(z)|\geq c>0$ uniformly. Indeed, $m(z)$ is continuous, this is equivalent to $m(z)\neq 0$, which can be verified as follows: $$m(z) = \frac{-z+\sqrt{z^2-4}}{2}=0 \Leftrightarrow \sqrt{z^2-4}=z$$
$$\Rightarrow z^2-4=z^2\Leftrightarrow -4=0$$

@@

\begin{equation*}
G_{xy} = G_{xy}^{(x)} - G_{xx}\sum_{k\neq x}H_{xk}G_{ky}^{(x)} =- G_{xx}\sum_{k\neq x}H_{xk}G_{ky}^{(x)}\quad x\neq y
\end{equation*}
Lastly, let us derive the derivatives of the resolvent w.r.t. to the matrix entry $H_{ij}$ using the limit definition. Let us define the perturbed matrix $H' = H(H_{ij}\mapsto H_{ij}+\epsilon)$ at entry $H_{ij}$, where $G' = (H'-z)^{-1}$ and let $\epsilon_{ij} = \mathbf{0}(0_{ij}\mapsto \epsilon)$ be the perturbed zero matrix, which we can write as $\mathbf{1}_{ij}$ when $\epsilon=1$. By our matrix identities, we have: $$\partial_{H_{ij}}G(z)_{xy}=\lim_{\epsilon\rightarrow 0} \frac{G_{xy}'-G_{xy}}{\epsilon} = \lim_{\epsilon\rightarrow 0}\frac{\left[G'(H-H')G\right]_{xy}}{\epsilon} = -\lim_{\epsilon\rightarrow 0}\frac{\left[G'\epsilon_{ij}G\right]_{xy}}{\epsilon} = -[G'\mathbf{1}_{ij}G]_{xy} = -G_{xi}G_{jy}$$
\begin{equation*}\label{resolventderivative}
\partial_{H_{ij}}\overline{G(z)_{xy}}= \lim_{\epsilon\rightarrow 0}\frac{\left[\overline{G'}(H^\intercal-H'^\intercal)\overline{G}\right]_{xy}}{\epsilon} =\\\\= -\lim_{\epsilon\rightarrow 0}\frac{\left[\overline{G'}\epsilon_{ji}\overline{G}\right]_{xy}}{\epsilon} = -[\overline{G'}\mathbf{1}_{ji}\overline{G}]_{xy} = -\overline{G_{xj}}\ \overline{G_{iy}}
\end{equation*}
By extension of the Hermitian property, we have $\partial_{\overline{H}_{ij}} \overline{G(z)_{xy}} = \partial_{{H}_{ji}} \overline{G(z)_{xy}}  = -\overline{G_{xi}}\ \overline{G_{jy}}$
\noindent Lastly, the following result is ubiquitous in RMT literature (8.3.iii \cite{dynamic}), and as such has its own name: 
\begin{boxtheorem}{Ward identity: }\label{ward} $$\sum_j |G_{ij}|^2 = \frac{1}{\eta}\im G_{ii}$$\end{boxtheorem}
The proof follows directly from the spectral decomposition of the resolvent we showed in $(1)$, by which:
$$G_{ij} = \sum_{\alpha} \frac{\mathbf{u}_\alpha(i) \mathbf{u}_\alpha^*(j)}{\lambda_\alpha - z}\quad \Leftrightarrow \sum_j G_{ij} G_{ji}^* = \sum_{j, \alpha, \beta}\frac{\mathbf{u}_\alpha(i) \mathbf{u}_\alpha^*(j)}{\lambda_\alpha - z} \frac{\mathbf{u}_\beta(j) \mathbf{u}_\beta^*(i)}{\lambda_\beta - z^*}
$$
And since the eigenvectors are orthogonal $\sum_j \mathbf{u}_\alpha^*(j) \mathbf{u}_\beta(j) = \delta_{\alpha\beta}$, we have: $$\sum_j |G_{ij}|^2=\sum_j G_{ij} G_{ji}^* = \sum_\alpha \frac{|\mathbf{u}_\alpha(i)|^2}{|\lambda_\alpha - z|^2}$$ 
We can also take the imaginary part of the first identity:
$$\text{Im}[G_{ii}] = \text{Im}\left[\sum_\alpha \frac{|\mathbf{u}_\alpha(i)|^2}{\lambda_\alpha - z}\right]
= \sum_\alpha \text{Im}\left[\frac{|\mathbf{u}_\alpha(i)|^2}{\lambda_\alpha - E - i\eta}\right]=\sum_\alpha \text{Im}\left[\frac{|\mathbf{u}_\alpha(i)|^2(\lambda_\alpha - E + i\eta)}{(\lambda_\alpha - E)^2 + \eta^2}\right]= $$
$$= \sum_\alpha \text{Im}\left[\frac{|\mathbf{u}_\alpha(i)|^2(\lambda_\alpha - E)}{(\lambda_\alpha - E)^2 + \eta^2} + \frac{|\mathbf{u}_\alpha(i)|^2 \cdot i\eta}{(\lambda_\alpha - E)^2 + \eta^2}\right] 
= \sum_\alpha \frac{|\mathbf{u}_\alpha(i)|^2 \cdot \eta}{(\lambda_\alpha - E)^2 + \eta^2} = \frac{1}{\eta} \sum_\alpha \frac{|\mathbf{u}_\alpha(i)|^2}{|\lambda_\alpha - z|^2}$$
$$\Rightarrow \sum_j |G_{ij}|^2 = \frac{1}{\eta}\im G_{ii}$$

@@

$$dG(t)_{xy} = \frac{\partial G(t)_{xy}}{\partial t}dt +\sqrt{S_{ij}}\sum_{i\leq j}\frac{\partial G(t)_{xy}}{\partial b(t)_{ij}}db(t)_{ij}
+\frac{S_{ij}}{2}\sum_{i\leq j}\frac{\partial^2 G(t)_{xy}}{\partial b(t)_{ij}^2}(db(t)_{ij})^2$$
To calculate the individual terms, we will use the definition of derivative:
$$\frac{\partial G(t)_{xy}}{\partial t}=\lim_{\epsilon\rightarrow 0}\frac{(H(t)-w(t+\epsilon))^{-1}_{xy}-(H(t)-w(t))^{-1}{xy}}{\epsilon},$$
whereas the following matrix identity: $A^{-1}-B^{-1} = A^{-1}(B-A)B^{-1}$ can help us approximate for small perturbations. Namely, for $\Delta w(t) = w(t+\epsilon)-w(t)$, we have:
$$\left[(H(t)-w(t+\epsilon))^{-1}\right]_{xy}-\left[(H(t)-w(t))^{-1}\right ]_{xy}= \left[ G(t)\Delta w(t) G(t)\right]_{xy}$$$$\Rightarrow \frac{\partial G(t)_{xy}}{\partial t} =\lim_{\epsilon\rightarrow 0} \frac{ \left[ G(t)\Delta w(t) G(t)\right]_{xy}}{\epsilon}=\sum_{j}G(t)_{xj}\frac{dw(t)}{dt}G(t)_{jy}= -m(z)\sum_j G(t)_{xj}G(t)_{jy}$$
Similarly, we can carry out the calculation for the second term, using the independence of entries:

@@

\subsection{Dynamical $T$-equation}
Having found the differential of the resolvent, we will now proceed with defining the time-dependent $T$-matrix as:
$$T(t)_{ab} = \sum_{x,y}S_{ax}^{\frac{1}{2}}F(t)_{xy}S_{yb}^{\frac{1}{2}},$$
where $F(t)_{xy} = |G(t)_{xy}|^2 = G(t)_{xy}\overline{G(t)_{xy}}$. 
Applying Itô's formula to \( F(t)_{xy} \), we have:
\[
dF(t)_{xy}= d|G_{xy}|^2= G(t)_{xy} d\overline{G(t)}_{xy} + \overline{G(t)}_{xy} dG(t)_{xy} + dG(t)_{xy} d\overline{G(t)}_{xy}.
\]
$$d|G_{xy}|^2 = G_{xy}d\overline{G_{xy}} + \overline{G}_{xy}dG_{xy} + d\left[G_{xy}, \overline{G}_{xy}\right]$$
 $$d|G_{xy}|^2 = G_{xy}d\overline{G_{xy}} + \overline{G}_{xy}dG_{xy} +d\left[\sum_{\alpha, \beta} G_{x\alpha}d H_{\alpha \beta}\overline{G}_{xy}\right]$$
$$d|G_{xy}|^2 = G_{xy}d\overline{G_{xy}} + \overline{G}_{xy}dG_{xy} +\sum_{\alpha,\beta, \gamma, \delta}G_{x\alpha}G_{\beta\gamma}\overline{G_{xy}}\overline{G_{\delta \gamma}}$$
In order to find the derivative of the $T$-matrix, we need to substitute for the earlier terms we found, namely \( dG(t)_{xy} = d\mathrm{I}(t)_{xy} + d\mathrm{II}(t)_{xy} dt \) and its conjugate, noting that \( d\mathrm{I}(t)_{xy} d\overline{\mathrm{I}(t)}_{xy} \) contributes to the quadratic variation, we obtain
\(
dF(t)_{xy} = dM(t)_{xy} + \Omega(t)_{xy} dt
\), where
\begin{equation*}
dM(t)_{xy} = \overline{G(t)}_{xy} d\mathrm{I}(t)_{xy} + G(t)_{xy} \overline{d\mathrm{I}(t)}_{xy} \end{equation*}
\begin{equation*}
\Omega(t)_{xy} = G_{xy}\frac{\overline{d\mathrm{II}(t)}_{xy}}{dt}+\overline{G_{xy}}\frac{d\mathrm{II}(t)_{xy}}{dt}+\frac{d\left[G_{xy}, \overline{G_{xy}}\right]}{dt}
\end{equation*}
and when expanded w.r.t to $d\mathrm{I}(t)$ and $d\mathrm{II}(t)dt$:
$$dM(t)_{xy} = \sum_{\alpha, \beta}\overline{G_{xy}}G_{x\alpha}{S_{\alpha\beta}}^{1/2}G_{\beta y}dB_{\beta(t)}+\sum_{\alpha, \beta}{G}_{xy}\overline{G_{x\alpha}}{S_{\alpha\beta}}^{1/2}\,\overline{G_{\beta y}}dB_{\beta(t)}$$

$$\Omega(t)_{xy}=G_{xy}(t)\left(\overline{\sum_j G_{xj}(t)S_{jy}(G_{yy}(t)-m(z))G_{jy}(t)}\right)+$$
$$+\overline{G_{xy}(t)}\left(\sum_j G_{xj}(t)S_{jy}(G_{yy}(t)-m(z))G_{jy}(t)\right)+\sum_{\alpha, \beta}|G_{xa}(t)|^2S_{\alpha, \beta}|G_{x\beta}(t)|^2$$
Hence, by Itô the $T$-equation becomes: 
\begin{equation*}
d{T} = {T}^2 dt + S^{1/2} dM_t(z)S^{1/2} + S^{1/2} \Omega_t(z) S^{1/2}dt \tag{3.1}
\end{equation*}
Now, define the \textit{time-dependent diffusion profile} as:$$\Theta_t = \frac{|m(z)|^2S}{1-t|m(z)|^2S}$$
Let us take its derivative w.r.t to $t$: 
$$\frac{d\Theta_t}{dt} = \frac{d}{dt}\frac{|m(z)|^2S}{1-t|m(z)|^2S} = \frac{-|m(z)|^2S(-|m(z)|^2S)}{(1-t|m(z)|^2S)^2} = \Theta_t^2 \Leftrightarrow d\Theta_t = \Theta_t^2 dt$$
Consider the fluctuation term $\mathcal{E}_t(z)$, i.e the difference between our $T$-matrix and the diffusion profile:
$$\E_t(z):T_t(z)-\Theta_t$$
We can compute its evolution equation $d\E_t(z) = dT_t(z)-d\Theta_t$ by substituting for what we found before:
$$\Rightarrow d\E_t(z) = T_t(z)^2dt - \Theta_t^2dt-S^{1/2}dM_t(z)S^{1/2}+S^{1/2}\Omega_t(z)S^{1/2}dt$$
But observe that:
$$T_t(z)^2-\Theta_t^2 =(\E_t(z)+\Theta_t(z))^2- \Theta_t(z)^2=\E_t(z)^2+\Theta_t\E_t(z)+\E_t(z)\Theta_t$$
\begin{equation*}\Rightarrow d\E_t(z)=\{\Theta_t \E_t(z)+\E_t(z)\Theta_t\}dt +\E_t^2(z)dt - S^{1/2} dM_t(z)S^{1/2} + S^{1/2}
 \Omega_t(z) S^{1/2}dt\tag{3.2}\end{equation*}
Now, observe that the first term $\{\Theta_t \E_t(z)+\E_t(z)\Theta_t\}dt$ makes this equation a matrix-valued linear SDE with a nonlinear stochastic term $W(t) = \E_t^2(z)dt - S^{1/2} dM_t(z)S^{1/2} + S^{1/2} \Omega_t(z) S^{1/2}dt$. This means that we have to apply a method of variation of parameters (a matrix-valued Duhamel formula \cite{bandSDE}). For this, let us identify an integrating factor $U(t, s)$. Observe that: 
$$\partial_{t}\{\text{Id}+(t-s)\Theta_t\} = \Theta_t+(t-s)\Theta_t^2=\Theta_t\frac{1-t|m(z)|^2S+(t-s)|m(z)|^2S}{1-t|m(z)|^2S}=$$
$$=\Theta_t \frac{1-s|m(z)|^2S}{1-t|m(z)|^2S}=\Theta_t\{\text{Id}+(t-s)\Theta_t\}$$
This is equivalent to $\partial_t U(t, s) = \Theta_t U(t, s)$, which makes $U(t, s)$ our evolution operator, since also $U(t, t) = \text{Id}$. We can then define the integral form: $\E_t(z) = \int_0^t U(t, s) W(s) U(t, s)ds,$ and verify that it satisfies our SDE by using Leibniz's integral rule, we get:
$$d\E_t(z) = U(t, t) W(t) U(t, t)dt + \int_0^t d\left[U(t, s)W(s)U(t, s)\right]ds=$$
$$=W(t)dt + \int_0^t\left[\Theta_t U(t, s) W(s) U(t, s) + U(t, s)W(s)U(t, s)\Theta_t\right]dtds =$$
$$= \E_t^2(z)dt - S^{1/2} dM_t(z)S^{1/2} + S^{1/2} \Omega_t(z) S^{1/2}dt + \{\Theta_t \E_t(z)+\E_t(z)\Theta_t\}dt$$
Therefore, by the pathwise uniqueness of solutions to SDEs (Thm. 9.1 \cite{steele}), the following expression satisfies the same SDE:\textcolor{red}{Define:
\begin{equation*}\E_t(z)=\E_t^{D}(z)+\E_t^{M}(z)+\E_t^{S}(z)\tag{3.3}\end{equation*}
$$\E_t^{D}(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\} S^{1/2} \Omega(s) S^{1/2} \{\text{Id} + (t-s)\Theta_t\}ds,$$
$$\E_t^{M}(z)=-\int_0^t \{\text{Id} + (t-s)\Theta_t\}S^{1/2} dM(s)S^{1/2}\{\text{Id} +(t-s)\Theta_t\}ds,$$
$$\E_t^{S}(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\}\E_s^2(z) \{\text{Id} + (t-s)\Theta_t\}ds,$$}

>>>>

\noindent In our analysis, we will utilize the flow method (\hyperref[sec:flow]{Section 3}), where the spectral parameter $z=E+i\eta$ of the resolvent of $H$ (defined in \hyperref[sec:prereq]{Section 2}) is varied at constant-speed in the upper-half plane $\mathbb{H}$ ($E\in\mathbb{R}$ and $\eta>0$) as the entries of $H$ are realized as Brownian motion \cite{bandSDE}. We will make two key assumptions. The first is a diffusion time scale of $\eta \asymp W^2 N^{-2}$ and the second is that $\eta\geq W^{-3/4+\eta}$ for some $\eta>0$. Those will be discussed in detail later on in Section 3.3.

@@

\subsection*{Stieltjes transform identities}
Let us establish several facts and lemmas that we will need throughout our later work. We can begin by observing that: $$m(z)(m(z)+z) = \frac{1}{4}(-z+\sqrt{z^2-4})(z+\sqrt{z^2-4})=\frac{1}{4}(-z^2+z^2-4)=-1$$
$$\Rightarrow |m(z)| = \frac{1}{|m(z)+z|^{-1}}$$
Now, take the imaginary part of $(2)$: $$\text{Im}(m(z)) + \text{Im}\left(\frac{1}{m(z)}\right)+\eta=0$$
We can calculate the second term by simply expanding: $$\frac{1}{m(z)} = \frac{1}{\text{Re}(m(z))+\text{Im}(m(z))i} = \frac{\text{Re}(m(z))-\text{Im}(m(z))i}{|m(z)|^2}\Leftrightarrow \text{Im}\left(\frac{1}{m(z)}\right) = -\frac{\text{Im}(m(z))}{|m(z)|^2}$$
$$\Rightarrow\text{Im}(m(z)) + \text{Im}\left(\frac{1}{m(z)}\right)+\eta=\text{Im}(m(z)) -\frac{\text{Im}(m(z))}{|m(z)|^2}+\eta=0$$
$$\Rightarrow \text{Im}(m(z))\left(1-\frac{1}{|m(z)|^2}\right)=-\eta$$
And since $\text{Im}(m(z))>0$ and $\eta>0$, we must have:
\begin{equation*}\label{2.1} 1-\frac{1}{|m(z)|^2}<0\quad \Leftrightarrow\quad |m(z)|<1, \tag{2.1}
\end{equation*}
which is also equivalent to $\text{Im }m \asymp 1$, where $\asymp$ means being bounded above and below up to a fixed, positive factor. Furthermore, let us rewrite the latter equation as the following two identities: \begin{equation*}\label{2.2}1-|m(z)|^2 = \frac{\eta|m(z)|^2}{\text{Im}(m(z))}
\tag{2.2}
\end{equation*}
\begin{equation*}\label{2.3}\text{Im}(m(z))= \frac{\eta|m(z)|^2}{1-|m(z)|^2 }
\tag{2.3}
\end{equation*}
Now, let $E\in [-10, 10]$ and $\eta\in (0, 10]$. We claim that $|m(z)|\geq c>0$ uniformly. Indeed, $m(z)$ is continuous, this is equivalent to $m(z)\neq 0$, which can be verified as follows: $$m(z) = \frac{-z+\sqrt{z^2-4}}{2}=0 \Leftrightarrow \sqrt{z^2-4}=z$$
$$\Rightarrow z^2-4=z^2\Leftrightarrow -4=0$$

@@

\begin{equation*}
G_{xy} = G_{xy}^{(x)} - G_{xx}\sum_{k\neq x}H_{xk}G_{ky}^{(x)} =- G_{xx}\sum_{k\neq x}H_{xk}G_{ky}^{(x)}\quad x\neq y
\end{equation*}
Lastly, let us derive the derivatives of the resolvent w.r.t. to the matrix entry $H_{ij}$ using the limit definition. Let us define the perturbed matrix $H' = H(H_{ij}\mapsto H_{ij}+\epsilon)$ at entry $H_{ij}$, where $G' = (H'-z)^{-1}$ and let $\epsilon_{ij} = \mathbf{0}(0_{ij}\mapsto \epsilon)$ be the perturbed zero matrix, which we can write as $\mathbf{1}_{ij} = \mathbf{e}_i^*\mathbf{e}_j$ when $\epsilon=1$. By our matrix identities, we have: $$\partial_{H_{ij}}G(z)_{xy}=\lim_{\epsilon\rightarrow 0} \frac{G_{xy}'-G_{xy}}{\epsilon} = \lim_{\epsilon\rightarrow 0}\frac{\left[G'(H-H')G\right]_{xy}}{\epsilon} = -\lim_{\epsilon\rightarrow 0}\frac{\left[G'\epsilon_{ij}G\right]_{xy}}{\epsilon} = -[G'\mathbf{1}_{ij}G]_{xy} = -G_{xi}G_{jy}$$
\begin{equation*}\label{resolventderivative}
\partial_{H_{ij}}\overline{G(z)_{xy}}= \lim_{\epsilon\rightarrow 0}\frac{\left[\overline{G'}(H^\intercal-H'^\intercal)\overline{G}\right]_{xy}}{\epsilon} =\\\\= -\lim_{\epsilon\rightarrow 0}\frac{\left[\overline{G'}\epsilon_{ji}\overline{G}\right]_{xy}}{\epsilon} = -[\overline{G'}\mathbf{1}_{ji}\overline{G}]_{xy} = -\overline{G_{xj}}\ \overline{G_{iy}}
\end{equation*}
By extension of the Hermitian property, we have $\partial_{\overline{H}_{ij}} \overline{G(z)_{xy}} = \partial_{{H}_{ji}} \overline{G(z)_{xy}}  = -\overline{G_{xi}}\ \overline{G_{jy}}$
\noindent Lastly, the following result is ubiquitous in RMT literature (8.3.(iii) \cite{dynamic}), and as such has its own name: 
\begin{boxtheorem}{Ward identity: }\label{ward} $$\sum_j |G_{ij}|^2 = \frac{1}{\eta}\im G_{ii}$$\end{boxtheorem}
The proof follows directly from the spectral decomposition of the resolvent we showed in $(1)$, by which:
$$G_{ij} = \sum_{\alpha} \frac{\mathbf{u}_\alpha(i) \mathbf{u}_\alpha^*(j)}{\lambda_\alpha - z}\quad \Leftrightarrow \sum_j G_{ij} G_{ji}^* = \sum_{j, \alpha, \beta}\frac{\mathbf{u}_\alpha(i) \mathbf{u}_\alpha^*(j)}{\lambda_\alpha - z} \frac{\mathbf{u}_\beta(j) \mathbf{u}_\beta^*(i)}{\lambda_\beta - z^*}
$$
And since the eigenvectors are orthogonal $\sum_j \mathbf{u}_\alpha^*(j) \mathbf{u}_\beta(j) = \delta_{\alpha\beta}$, we have: $$\sum_j |G_{ij}|^2=\sum_j G_{ij} G_{ji}^* = \sum_\alpha \frac{|\mathbf{u}_\alpha(i)|^2}{|\lambda_\alpha - z|^2}$$ 
We can also take the imaginary part of the first identity:
$$\text{Im}[G_{ii}] = \text{Im}\left[\sum_\alpha \frac{|\mathbf{u}_\alpha(i)|^2}{\lambda_\alpha - z}\right]
= \sum_\alpha \text{Im}\left[\frac{|\mathbf{u}_\alpha(i)|^2}{\lambda_\alpha - E - i\eta}\right]=\sum_\alpha \text{Im}\left[\frac{|\mathbf{u}_\alpha(i)|^2(\lambda_\alpha - E + i\eta)}{(\lambda_\alpha - E)^2 + \eta^2}\right]= $$
$$= \sum_\alpha \text{Im}\left[\frac{|\mathbf{u}_\alpha(i)|^2(\lambda_\alpha - E)}{(\lambda_\alpha - E)^2 + \eta^2} + \frac{|\mathbf{u}_\alpha(i)|^2 \cdot i\eta}{(\lambda_\alpha - E)^2 + \eta^2}\right] 
= \sum_\alpha \frac{|\mathbf{u}_\alpha(i)|^2 \cdot \eta}{(\lambda_\alpha - E)^2 + \eta^2} = \frac{1}{\eta} \sum_\alpha \frac{|\mathbf{u}_\alpha(i)|^2}{|\lambda_\alpha - z|^2}$$
$$\Rightarrow \sum_j |G_{ij}|^2 = \frac{1}{\eta}\im G_{ii}$$

@@

$$dG(t)_{xy} = \frac{\partial G(t)_{xy}}{\partial t}dt +\sqrt{S_{ij}}\sum_{i\leq j}\frac{\partial G(t)_{xy}}{\partial b(t)_{ij}}db(t)_{ij}
+\frac{S_{ij}}{2}\sum_{i\leq j}\frac{\partial^2 G(t)_{xy}}{\partial b(t)_{ij}^2}(db(t)_{ij})^2$$
To calculate the individual terms, we will use the definition of derivative:
$$\frac{\partial G(t)_{xy}}{\partial t}=\lim_{\epsilon\rightarrow 0}\frac{(H(t)-w(t+\epsilon))^{-1}_{xy}-(H(t)-w(t))^{-1}{xy}}{\epsilon}.$$
The matrix identity $(2.4)$ can help us approximate for small perturbations $\Delta w(t) = w(t+\epsilon)-w(t)$:
$$\left[(H(t)-w(t+\epsilon))^{-1}\right]_{xy}-\left[(H(t)-w(t))^{-1}\right ]_{xy}= \left[ G(t)\Delta w(t) G(t)\right]_{xy}$$$$\Rightarrow \frac{\partial G(t)_{xy}}{\partial t} =\lim_{\epsilon\rightarrow 0} \frac{ \left[ G(t)\Delta w(t) G(t)\right]_{xy}}{\epsilon}=\sum_{j}G(t)_{xj}\frac{dw(t)}{dt}G(t)_{jy}= -m(z)\sum_j G(t)_{xj}G(t)_{jy}$$
Similarly, we can carry out the calculation for the second term, using the independence of entries:

@@

\subsection{Dynamical $T$-equation}
Having found the differential of the resolvent, we will now proceed with defining the time-dependent $T$-matrix as:
$$T(t)_{ab} = \sum_{x,y}S_{ax}^{\frac{1}{2}}F(t)_{xy}S_{yb}^{\frac{1}{2}},$$
where $F(t)_{xy} = |G(t)_{xy}|^2 = G(t)_{xy}\overline{G(t)_{xy}}$. 
Applying Itô's formula to \( F(t)_{xy} \), we have:
\[
dF(t)_{xy}= d|G_{xy}|^2= G(t)_{xy} d\overline{G(t)}_{xy} + \overline{G(t)}_{xy} dG(t)_{xy} + dG(t)_{xy} d\overline{G(t)}_{xy}.
\]
$$d|G_{xy}|^2 = G_{xy}d\overline{G_{xy}} + \overline{G}_{xy}dG_{xy} + d\left[G_{xy}, \overline{G}_{xy}\right]$$
 $$d|G_{xy}|^2 = G_{xy}d\overline{G_{xy}} + \overline{G}_{xy}dG_{xy} +d\left[\sum_{\alpha, \beta} G_{x\alpha}d H_{\alpha \beta}\overline{G}_{xy}\right]$$
$$d|G_{xy}|^2 = G_{xy}d\overline{G_{xy}} + \overline{G}_{xy}dG_{xy} +\sum_{\alpha,\beta, \gamma, \delta}G_{x\alpha}G_{\beta\gamma}\overline{G_{xy}}\overline{G_{\delta \gamma}}$$
In order to find the derivative of the $T$-matrix, we need to substitute for the earlier terms we found, namely \( dG(t)_{xy} = d\mathrm{I}(t)_{xy} + d\mathrm{II}(t)_{xy} dt \) and its conjugate. By observing that \( d\mathrm{I}(t)_{xy} d\overline{\mathrm{I}(t)}_{xy} \) contributes to the quadratic variation, we can obtain the following expression:
\[
dF(t)_{xy} = dM(t)_{xy} + \Omega(t)_{xy} dt,
\]
where:
\begin{equation*}
dM(t)_{xy} = \overline{G(t)}_{xy} d\mathrm{I}(t)_{xy} + G(t)_{xy} \overline{d\mathrm{I}(t)}_{xy} \end{equation*}
\begin{equation*}
\Omega(t)_{xy} = G_{xy}\frac{\overline{d\mathrm{II}(t)}_{xy}}{dt}+\overline{G_{xy}}\frac{d\mathrm{II}(t)_{xy}}{dt}+\frac{d\left[G_{xy}, \overline{G_{xy}}\right]}{dt}
\end{equation*}
When expanded w.r.t to $d\mathrm{I}(t)$ and $d\mathrm{II}(t)dt$, those terms are:
$$dM(t)_{xy} = \sum_{\alpha, \beta}\overline{G_{xy}}G_{x\alpha}{S_{\alpha\beta}}^{1/2}G_{\beta y}dB_{\beta(t)}+\sum_{\alpha, \beta}{G}_{xy}\overline{G_{x\alpha}}{S_{\alpha\beta}}^{1/2}\,\overline{G_{\beta y}}dB_{\beta(t)}$$
